SETI in the Spatio-Temporal Survey Domain \\ {\color{red} {\bf DRAFT} }

### 2019-05-29 paper/ms.tex
update figure names for submission
add bib

%\keywords{stars: activity --- stars: low-mass --- planets and satellites: detection}

@@

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{../figures/optical_haystack}
\caption{
Comparison of the 8-D ``Cosmic Haystack'' SETI search volume fraction, defined by \citet{wright2018c}, computed using five optical surveys with varying designs. The Haystack fraction covered by these optical surveys is 1-2 dex larger than typical SETI programs conducted in the radio.
Evryscope \citet{law2015} is the best survey considered here for SETI work, narrowly beating LSST due to its wide field of view and very dense light curves.}
\label{fig:hay}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{../figures/2ptcf.pdf}
\caption{two point correlation function of transiting exoplanets versus all stars in the kepler field. No obvious signs of engineering of the exoplanet population as a whole. exoplanets are actually slightly less correlated on small size scales than stars in general, which may be an artifact of detected planets being around brighter stars in the sample (i.e. having lower total density). 
While overly simple, this example demonstrates one possible test that could be done using existing and future exoplanet surveys.}
\label{fig:2pt}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{../figures/Kplanets.pdf}
\caption{Fractional range of orbital periods versus the mean angular separation for KNN clusters in (RA, Dec) space of transiting exoplanet systems in \Kepler. This sample only includes systems with only a single known transiting exoplanet. These KNN clusters have typical spatial separations of $\sim$0.1 deg. For $K$=3, three unique clusters have a spread in their orbital periods below 6\% (red points). However this is not a significant outlier in the orbital period similarity, and these clusters are not unusually close together in their spatial separation.}
\label{fig:knn}
\end{figure}

@@

\bibliography{/Users/james/Dropbox/references}

>>>>

@@

\begin{figure}[]
\centering
\includegraphics[width=3.5in]{fig1}
\caption{
Comparison of the 8-D ``Cosmic Haystack'' SETI search volume fraction, defined by \citet{wright2018c}, computed using five optical surveys with varying designs. The Haystack fraction covered by these optical surveys is 1-2 dex larger than typical SETI programs conducted in the radio.
Evryscope \citet{law2015} is the best survey considered here for SETI work, narrowly beating LSST due to its wide field of view and very dense light curves.}
\label{fig:hay}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{fig2}
\caption{two point correlation function of transiting exoplanets versus all stars in the kepler field. No obvious signs of engineering of the exoplanet population as a whole. exoplanets are actually slightly less correlated on small size scales than stars in general, which may be an artifact of detected planets being around brighter stars in the sample (i.e. having lower total density). 
While overly simple, this example demonstrates one possible test that could be done using existing and future exoplanet surveys.}
\label{fig:2pt}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{fig3}
\caption{Fractional range of orbital periods versus the mean angular separation for KNN clusters in (RA, Dec) space of transiting exoplanet systems in \Kepler. This sample only includes systems with only a single known transiting exoplanet. These KNN clusters have typical spatial separations of $\sim$0.1 deg. For $K$=3, three unique clusters have a spread in their orbital periods below 6\% (red points). However this is not a significant outlier in the orbital period similarity, and these clusters are not unusually close together in their spatial separation.}
\label{fig:knn}
\end{figure}

@@

%\bibliography{/Users/james/Dropbox/references}
\begin{thebibliography}{}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Arnold}(2005)}]{arnold2005}
{Arnold}, L. 2005, in SF2A-2005: Semaine de l'Astrophysique Francaise, ed.
  F.~{Casoli}, T.~{Contini}, J.~M. {Hameury}, \& L.~{Pagani}, 207

\bibitem[{{Astropy Collaboration} {et~al.}(2013){Astropy Collaboration},
  {Robitaille}, {Tollerud}, {Greenfield}, {Droettboom}, {Bray}, {Aldcroft},
  {Davis}, {Ginsburg}, {Price-Whelan}, {Kerzendorf}, {Conley}, {Crighton},
  {Barbary}, {Muna}, {Ferguson}, {Grollier}, {Parikh}, {Nair}, {Unther},
  {Deil}, {Woillez}, {Conseil}, {Kramer}, {Turner}, {Singer}, {Fox}, {Weaver},
  {Zabalza}, {Edwards}, {Azalee Bostroem}, {Burke}, {Casey}, {Crawford},
  {Dencheva}, {Ely}, {Jenness}, {Labrie}, {Lim}, {Pierfederici}, {Pontzen},
  {Ptak}, {Refsdal}, {Servillat}, \& {Streicher}}]{astropy}
{Astropy Collaboration}, {Robitaille}, T.~P., {Tollerud}, E.~J., {et~al.} 2013,
  \aap, 558, A33

\bibitem[{{Bellm}(2014)}]{bellm2014}
{Bellm}, E. 2014, in The Third Hot-wiring the Transient Universe Workshop, ed.
  P.~R. {Wozniak}, M.~J. {Graham}, A.~A. {Mahabal}, \& R.~{Seaman}, 27--33

\bibitem[{{Berea} {et~al.}(2019){Berea}, {Croft}, \& {Angerhausen}}]{berea2019}
{Berea}, A., {Croft}, S., \& {Angerhausen}, D. 2019, arXiv e-prints,
  arXiv:1903.08381

\bibitem[{{Borucki} {et~al.}(2010){Borucki}, {Koch}, {Basri}, {Batalha},
  {Brown}, {Caldwell}, {Caldwell}, {Christensen-Dalsgaard}, {Cochran},
  {DeVore}, {Dunham}, {Dupree}, {Gautier}, {Geary}, {Gilliland}, {Gould},
  {Howell}, {Jenkins}, {Kondo}, {Latham}, {Marcy}, {Meibom}, {Kjeldsen},
  {Lissauer}, {Monet}, {Morrison}, {Sasselov}, {Tarter}, {Boss}, {Brownlee},
  {Owen}, {Buzasi}, {Charbonneau}, {Doyle}, {Fortney}, {Ford}, {Holman},
  {Seager}, {Steffen}, {Welsh}, {Rowe}, {Anderson}, {Buchhave}, {Ciardi},
  {Walkowicz}, {Sherry}, {Horch}, {Isaacson}, {Everett}, {Fischer}, {Torres},
  {Johnson}, {Endl}, {MacQueen}, {Bryson}, {Dotson}, {Haas}, {Kolodziejczak},
  {Van Cleve}, {Chandrasekaran}, {Twicken}, {Quintana}, {Clarke}, {Allen},
  {Li}, {Wu}, {Tenenbaum}, {Verner}, {Bruhweiler}, {Barnes}, \&
  {Prsa}}]{borucki2010}
{Borucki}, W.~J., {Koch}, D., {Basri}, G., {et~al.} 2010, Science, 327, 977

\bibitem[{{Boyajian} {et~al.}(2015){Boyajian}, {LaCourse}, {Rappaport},
  {Fabrycky}, {Fischer}, {Gandolfi}, {Kennedy}, {Liu}, {Moor}, {Olah}, {Vida},
  {Wyatt}, {Best}, {Ciesla}, {Csak}, {Dupuy}, {Handler}, {Heng}, {Korhonen},
  {Kovacs}, {Kozakis}, {Kriskovics}, {Schmitt}, {Szabo}, {Szabo}, {Wang},
  {Goodman}, {Hoekstra}, \& {Jek}}]{boyajian2015}
{Boyajian}, T.~S., {LaCourse}, D.~M., {Rappaport}, S.~A., {et~al.} 2015, ArXiv
  e-prints, arXiv:1509.03622

\bibitem[{Council(2010)}]{astro2010}
Council, N.~R. 2010, New Worlds, New Horizons in Astronomy and Astrophysics
  (Washington, DC: The National Academies Press), doi:10.17226/12951

\bibitem[{{Djorgovski}(2000)}]{djorgovski2000}
{Djorgovski}, S. 2000, in Astronomical Society of the Pacific Conference
  Series, Vol. 213, Bioastronomy 99, ed. G.~{Lemarchand} \& K.~{Meech}, 519

\bibitem[{{Djorgovski} {et~al.}(2013){Djorgovski}, {Mahabal}, {Drake},
  {Graham}, \& {Donalek}}]{djorgovski2013}
{Djorgovski}, S.~G., {Mahabal}, A., {Drake}, A., {Graham}, M., \& {Donalek}, C.
  2013, {Sky Surveys}, ed. T.~D. {Oswalt} \& H.~E. {Bond}, 223

\bibitem[{{Drake} {et~al.}(2009){Drake}, {Djorgovski}, {Mahabal}, {Beshore},
  {Larson}, {Graham}, {Williams}, {Christensen}, {Catelan}, {Boattini},
  {Gibbs}, {Hill}, \& {Kowalski}}]{catalina}
{Drake}, A.~J., {Djorgovski}, S.~G., {Mahabal}, A., {et~al.} 2009, \apj, 696,
  870

\bibitem[{Forgan(2019)}]{forgan2019}
Forgan, D. 2019, Research Notes of the {AAS}, 3, 32

\bibitem[{{Forgan}(2017)}]{forgan2017}
{Forgan}, D.~H. 2017, ArXiv e-prints, arXiv:1707.03730

\bibitem[{{Heller} \& {Pudritz}(2016)}]{heller2016}
{Heller}, R., \& {Pudritz}, R.~E. 2016, Astrobiology, 16, 259

\bibitem[{{Howard} {et~al.}(2004){Howard}, {Horowitz}, {Wilkinson}, {Coldwell},
  {Groth}, {Jarosik}, {Latham}, {Stefanik}, {Willman}, {Wolff}, \&
  {Zajac}}]{howard2004}
{Howard}, A.~W., {Horowitz}, P., {Wilkinson}, D.~T., {et~al.} 2004, \apj, 613,
  1270

\bibitem[{Hunter(2007)}]{matplotlib}
Hunter, J.~D. 2007, Computing In Science \& Engineering, 9, 90

\bibitem[{{Isaacson} {et~al.}(2019){Isaacson}, {Siemion}, {Marcy}, {Hickish},
  {Price}, {Enriquez}, \& {Gizani}}]{isaacson2019}
{Isaacson}, H., {Siemion}, A.~P.~V., {Marcy}, G.~W., {et~al.} 2019, \pasp, 131,
  014201

\bibitem[{{Isaacson} {et~al.}(2017){Isaacson}, {Siemion}, {Marcy}, {Lebofsky},
  {Price}, {MacMahon}, {Croft}, {DeBoer}, {Hickish}, {Werthimer}, {Sheikh},
  {Hellbourg}, \& {Enriquez}}]{isaacson2017}
---. 2017, \pasp, 129, 054501

\bibitem[{{Ivezi{\'c}} {et~al.}(2014){Ivezi{\'c}}, {Connolly}, {Vanderplas}, \&
  {Gray}}]{astroMLText}
{Ivezi{\'c}}, {\v Z}., {Connolly}, A., {Vanderplas}, J., \& {Gray}, A. 2014,
  Statistics, Data Mining and Machine Learning in Astronomy (Princeton
  University Press)

\bibitem[{{Ivezi{\'c}} {et~al.}(2008){Ivezi{\'c}}, {Tyson}, {Acosta},
  {Allsman}, {Anderson}, {Andrew}, {Angel}, {Axelrod}, {Barr}, {Becker},
  {Becla}, {Beldica}, {Blandford}, {Bloom}, {Borne}, {Brandt}, {Brown},
  {Bullock}, {Burke}, {Chandrasekharan}, {Chesley}, {Claver}, {Connolly},
  {Cook}, {Cooray}, {Covey}, {Cribbs}, {Cutri}, {Daues}, {Delgado}, {Ferguson},
  {Gawiser}, {Geary}, {Gee}, {Geha}, {Gibson}, {Gilmore}, {Gressler}, {Hogan},
  {Huffer}, {Jacoby}, {Jain}, {Jernigan}, {Jones}, {Juric}, {Kahn}, {Kalirai},
  {Kantor}, {Kessler}, {Kirkby}, {Knox}, {Krabbendam}, {Krughoff}, {Kulkarni},
  {Lambert}, {Levine}, {Liang}, {Lim}, {Lupton}, {Marshall}, {Marshall}, {May},
  {Miller}, {Mills}, {Monet}, {Neill}, {Nordby}, {O'Connor}, {Oliver},
  {Olivier}, {Olsen}, {Owen}, {Peterson}, {Petry}, {Pierfederici},
  {Pietrowicz}, {Pike}, {Pinto}, {Plante}, {Radeka}, {Rasmussen}, {Ridgway},
  {Rosing}, {Saha}, {Schalk}, {Schindler}, {Schneider}, {Schumacher}, {Sebag},
  {Seppala}, {Shipsey}, {Silvestri}, {Smith}, {Smith}, {Strauss}, {Stubbs},
  {Sweeney}, {Szalay}, {Thaler}, {Vanden Berk}, {Walkowicz}, {Warner},
  {Willman}, {Wittman}, {Wolff}, {Wood-Vasey}, {Yoachim}, {Zhan}, \& {for the
  LSST Collaboration}}]{lsst}
{Ivezi{\'c}}, {\v Z}., {Tyson}, J.~A., {Acosta}, E., {et~al.} 2008, ArXiv
  e-prints, \# 0805.2366, arXiv:0805.2366

\bibitem[{Jones {et~al.}(2001--)Jones, Oliphant, Peterson, {et~al.}}]{scipy}
Jones, E., Oliphant, T., Peterson, P., {et~al.} 2001--, {SciPy}: Open source
  scientific tools for {Python}, , , [Online; accessed <today>]

\bibitem[{{Juric}(2012)}]{juric2012}
{Juric}, M. 2012, {LSD: Large Survey Database framework}, , , ascl:1209.003

\bibitem[{{Kipping} \& {Teachey}(2016)}]{kipping2016}
{Kipping}, D.~M., \& {Teachey}, A. 2016, \mnras, 459, 1233

\bibitem[{{Lacki}(2019)}]{lacki2019}
{Lacki}, B.~C. 2019, arXiv e-prints, arXiv:1903.05839

\bibitem[{{Landy} \& {Szalay}(1993)}]{landy1993}
{Landy}, S.~D., \& {Szalay}, A.~S. 1993, \apj, 412, 64

\bibitem[{{Law} {et~al.}(2015){Law}, {Fors}, {Ratzloff}, {Wulfken},
  {Kavanaugh}, {Sitar}, {Pruett}, {Birchard}, {Barlow}, {Cannon}, {Cenko},
  {Dunlap}, {Kraus}, \& {Maccarone}}]{law2015}
{Law}, N.~M., {Fors}, O., {Ratzloff}, J., {et~al.} 2015, \pasp, 127, 234

\bibitem[{{Lemarchand}(1994)}]{lemarchand1994}
{Lemarchand}, G.~A. 1994, \apss, 214, 209

\bibitem[{{Makovetskii}(1977)}]{makovetskii1977}
{Makovetskii}, P.~V. 1977, \sovast, 21, 251

\bibitem[{{Mamajek}(2017)}]{mamajek2017}
{Mamajek}, E. 2017, Research Notes of the American Astronomical Society, 1, 21

\bibitem[{McKinney(2010)}]{pandas}
McKinney, W. 2010, in Proceedings of the 9th Python in Science Conference, ed.
  S.~van~der Walt \& J.~Millman, 51 -- 56

\bibitem[{Oliphant(2007)}]{numpy}
Oliphant, T.~E. 2007, Computing in Science Engineering, 9, 10

\bibitem[{{Patterson} {et~al.}(2019){Patterson}, {Bellm}, {Rusholme}, {Masci},
  {Juric}, {Krughoff}, {Golkhou}, {Graham}, {Kulkarni}, {Helou}, \& {Zwicky
  Transient Facility Collaboration}}]{patterson2019}
{Patterson}, M.~T., {Bellm}, E.~C., {Rusholme}, B., {et~al.} 2019, \pasp, 131,
  018001

\bibitem[{P\'erez \& Granger(2007)}]{ipython}
P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9,
  21

\bibitem[{{Price} {et~al.}(2018){Price}, {MacMahon}, {Lebofsky}, {Croft},
  {DeBoer}, {Enriquez}, {Foster}, {Gajjar}, {Hellbourg}, {Isaacson}, {Siemion},
  {Werthimer}, {Green}, {Amy}, {Ball}, {Bock}, {Craig}, {Edwards}, {Jameson},
  {Mader}, {Preisig}, {Smith}, {Reynolds}, \& {Sarkissian}}]{price2018}
{Price}, D.~C., {MacMahon}, D.~H.~E., {Lebofsky}, M., {et~al.} 2018, ArXiv
  e-prints, arXiv:1804.04571

\bibitem[{{Ricker} {et~al.}(2015){Ricker}, {Winn}, {Vanderspek}, {Latham},
  {Bakos}, {Bean}, {Berta-Thompson}, {Brown}, {Buchhave}, {Butler}, {Butler},
  {Chaplin}, {Charbonneau}, {Christensen-Dalsgaard}, {Clampin}, {Deming},
  {Doty}, {De Lee}, {Dressing}, {Dunham}, {Endl}, {Fressin}, {Ge}, {Henning},
  {Holman}, {Howard}, {Ida}, {Jenkins}, {Jernigan}, {Johnson}, {Kaltenegger},
  {Kawai}, {Kjeldsen}, {Laughlin}, {Levine}, {Lin}, {Lissauer}, {MacQueen},
  {Marcy}, {McCullough}, {Morton}, {Narita}, {Paegert}, {Palle}, {Pepe},
  {Pepper}, {Quirrenbach}, {Rinehart}, {Sasselov}, {Sato}, {Seager},
  {Sozzetti}, {Stassun}, {Sullivan}, {Szentgyorgyi}, {Torres}, {Udry}, \&
  {Villasenor}}]{tess}
{Ricker}, G.~R., {Winn}, J.~N., {Vanderspek}, R., {et~al.} 2015, Journal of
  Astronomical Telescopes, Instruments, and Systems, 1, 014003

\bibitem[{Schwamb {et~al.}(2019)Schwamb, Hsieh, Bannister, Bodewits, Chesley,
  Fraser, Granvik, Jones, Juri{\'{c}}, Kelley, Ragozzine, Trilling, \&
  and}]{schwamb2019}
Schwamb, M.~E., Hsieh, H., Bannister, M.~T., {et~al.} 2019, Research Notes of
  the {AAS}, 3, 51

\bibitem[{{Shostak}(2004)}]{shostak2004}
{Shostak}, S. 2004, in IAU Symposium, Vol. 213, Bioastronomy 2002: Life Among
  the Stars, ed. R.~{Norris} \& F.~{Stootman}, 409

\bibitem[{{Tarter}(2001)}]{tarter2001}
{Tarter}, J. 2001, \araa, 39, 511

\bibitem[{{Tingay} {et~al.}(2018){Tingay}, {Tremblay}, \& {Croft}}]{tingay2018}
{Tingay}, S.~J., {Tremblay}, C.~D., \& {Croft}, S. 2018, \apj, 856, 31

\bibitem[{{Villarroel} {et~al.}(2016){Villarroel}, {Imaz}, \&
  {Bergstedt}}]{villarroel2016}
{Villarroel}, B., {Imaz}, I., \& {Bergstedt}, J. 2016, \aj, 152, 76

\bibitem[{{Wang} {et~al.}(2013){Wang}, {Brunner}, \& {Dolence}}]{wang2013}
{Wang}, Y., {Brunner}, R.~J., \& {Dolence}, J.~C. 2013, \mnras, 432, 1961

\bibitem[{{Worden} {et~al.}(2017){Worden}, {Drew}, {Siemion}, {Werthimer},
  {DeBoer}, {Croft}, {MacMahon}, {Lebofsky}, {Isaacson}, {Hickish}, {Price},
  {Gajjar}, \& {Wright}}]{worden2017}
{Worden}, S.~P., {Drew}, J., {Siemion}, A., {et~al.} 2017, Acta Astronautica,
  139, 98

\bibitem[{{Wright}(2017)}]{wright2017}
{Wright}, J.~T. 2017, {Exoplanets and SETI}, 186

\bibitem[{{Wright} {et~al.}(2016){Wright}, {Cartier}, {Zhao}, {Jontof-Hutter},
  \& {Ford}}]{wright2016}
{Wright}, J.~T., {Cartier}, K.~M.~S., {Zhao}, M., {Jontof-Hutter}, D., \&
  {Ford}, E.~B. 2016, \apj, 816, 17

\bibitem[{{Wright} {et~al.}(2018){Wright}, {Kanodia}, \& {Lubar}}]{wright2018c}
{Wright}, J.~T., {Kanodia}, S., \& {Lubar}, E. 2018, \aj, 156, 260

\bibitem[{{Wright} \& {Oman-Reagan}(2018)}]{wright2018b}
{Wright}, J.~T., \& {Oman-Reagan}, M.~P. 2018, International Journal of
  Astrobiology, 17, 177

\bibitem[{{Ze{\v{c}}evi{\'c}} {et~al.}(2019){Ze{\v{c}}evi{\'c}}, {Slater},
  {Juri{\'c}}, {Connolly}, {Lon{\v{c}}ari{\'c}}, {Bellm}, {Golkhou}, \&
  {Suberlak}}]{zecevic2019}
{Ze{\v{c}}evi{\'c}}, P., {Slater}, C.~T., {Juri{\'c}}, M., {et~al.} 2019, arXiv
  e-prints, arXiv:1905.09034

\end{thebibliography}
